---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# downloader

<!-- badges: start -->

<!-- badges: end -->

An improved `download.file` function that:

-   retries to download the file multiple times with or without a **delay**.
-   checks if the file to download already exists in the path and decide if overwrite it.
-   provides a full log with info regarding warning and errors of each download.

## Installation

You can install the development version of downloader with:

``` r
devtools::install_github("c1au6i0/downloader")
```

## Example

This is a basic example

```{r}
library(downloader)

# 2 csv files to download
to_download <- c(
  "https://www.stats.govt.nz/assets/Uploads/Business-employment-data/Business-employment-data-September-2022-quarter/Download-data/Business-employment-data-september-2022-quarter-csv.zip", 
  "www.stats.govt.nz/assets/Uploads/Business-financial-data/Business-financial-data-September-2022-quarter/Download-data/business-financial-data-september-2022-quarter-csv.zip"
  )
logs_download <- retry_download(conn  = to_download, 
               max_attempts = 5, 
               sleep_time = 1, 
               dest_path = tempdir(),  
               )
```


Here the logs generated:

```{r}
logs_download
```

